---
title: "Sentiment Analysis for Tesla Tweets & Relationship with Daily Stock Price Change"
author: "Li Peishan"
date: "3/30/2021"
output:
  html_notebook:
    toc: yes
    theme: journal
---
<style>
body{ /* Normal */
font-size: 15px;
color: black;
}
write {  
line-height: 7em;
}
table { /* Table */
font-size: 12px;
}
h1 { /* Header 1 */
font-size: 30px;
}
h2 { /* Header 2 *
font-size: 26px;
}
h3 { /* Header 3 */
font-size: 22px;
}
code.r{ /* Code block */
font-size: 14px;
}
pre { /* Code block */
font-size: 14px
}
.main-container {
    width: 80%;
    max-width: unset;
}
</style>

```{r setup, echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval=TRUE, message=FALSE, warning=FALSE)
```

Load packages:
```{r, echo=TRUE, eval=TRUE}
library(readxl)
library(magrittr)
library(dplyr)
library(ggplot2)    
library(ggmap)
library(ggthemes)
library(ggpubr)
library(ggforce)
library(tidyverse)
library(gmodels)
library(rgdal)
library(osmdata)
library(nominatim)
library(jsonlite)
library(RColorBrewer)
library(tidyr)
library(leaflet)
library(maps)
library(tigris)
library(tidytext)
library(textdata)
library(tm)
library(quanteda)
library(rvest)
library(stringr)
library(SnowballC)
library(wordcloud)
library(plotrix)
library(qdapDictionaries)
library(formattable)
library(stringr)
library(DT)
```

Import database:
```{r import data, echo=TRUE, eval=TRUE}
Tesla<-read.csv("/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/(update)TSLA_sentiment_analysis.csv")
```

# Cleaning the text and word cloud

## Text cleaning--Further remove numbers and punctuations

Create and preprocess text in corpus (162 tweets)
```{r create a dtm, echo=TRUE, eval=TRUE}
doc_id<-c(1:126)
line<-c(rep(1,126))
text<-data.frame(doc_id, text=Tesla$tweet,line, stringsAsFactors=FALSE)
df_source<-DataframeSource(text)
df_corpus<-VCorpus(df_source)
#Clean text
#removefullycap<-function(x){gsub("[A-Z][A-Z]+", " ", x)}
#removeemoji<-function(x){gsub("[^\x01-\x7F]", "", x)}
clean_corpus<-function(corpus){
  #corpus<-tm_map(corpus, content_transformer(removefullycap))
  #corpus<-tm_map(corpus, content_transformer(removeemoji))
  #corpus<-tm_map(corpus, content_transformer(tolower))
  #corpus<-tm_map(corpus, removeWords, c(stopwords("en")))
  corpus<-tm_map(corpus, removeNumbers)
  corpus<-tm_map(corpus, removePunctuation)
  corpus<-tm_map(corpus, stripWhitespace)
  return(corpus)
}
corpus_clean<-clean_corpus(df_corpus)
corpus_dtm<-DocumentTermMatrix(corpus_clean)
corpus_m<-as.matrix(corpus_dtm)
corpus_dtm
dim(corpus_m)
```

## Word cloud

Calculate tf_itf scores for tweets.
```{r frequncies, echo=TRUE, eval=TRUE}
#Tidy objects
corpustd<-tidy(corpus_dtm)
#Calculate frequencies
corpustf_idf<-corpustd %>%
  bind_tf_idf(term, document, count) %>%
  arrange(desc(tf_idf))
corpustf_idf
```

Word cloud for Tesla CEO's tweets
```{r word clouds, echo=TRUE, eval=TRUE}
purple_orange<-brewer.pal(10, "PuOr")
purple_orange<-purple_orange[-(1:2)]
set.seed(2200)
wordcloud(corpustf_idf$term, corpustf_idf$tf, max.words=100, colors=purple_orange)
```

# Sentiment

## (a) Stay positive

Calculate the tone of each text based on the positive and negative words that are being used in the tweets.

First build the sentiment function. Obtain the list of `positive.words` and `negative.words` from the sentiment dictionary of Hu & Liu (2004) using the `qdapDictionaries` package.
```{r sentiment function, echo=TRUE, eval=TRUE}
sentiment<-function(words=c("really great good stuff bad")){
  tok<-tokens(words)
  pos.count<-sum(tok[[1]] %in% positive.words)
  #cat("\n positive words:",tok[[1]][which(tok[[1]]%in%positive.words)],"\n")
  neg.count<-sum(tok[[1]]%in%negative.words)
  #cat("\n negative words:",tok[[1]][which(tok[[1]]%in%negative.words)],"\n")
  out<-(pos.count-neg.count)/(pos.count+neg.count)
  #cat("\n Tone of Document:",out)
  return(out)
}
```

Apply the function on text of the 162 tweets.
```{r tone of document, echo=TRUE, eval=TRUE}
toneofdocument<-Tesla
toneofdocument<-toneofdocument
for (i in 1:126){
  toneofdocument$toneofdocument[i]<-sentiment(toneofdocument$tweet[i])
}
toneofdocument
```

```{r write csv, echo=TRUE, eval=TRUE}
write.csv(toneofdocument,"/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Tesla tone of document.csv", row.names = FALSE)
```

Visualize the relationship between tone of the document and daily stock price change.
```{r visualize the relationship, echo=TRUE, eval=TRUE, fig.height=3,fig.width=5}
plot<-toneofdocument %>%
  ggplot(aes(x=toneofdocument,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Tone of Document", y="Daily stock price change", title="Relationship between Tone of Document and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5, angle=45,size=4.5))+
  coord_flip()
plot
```

## (b) Positive VS Negative

Ignore all documents that do not have words contained within the Hu & Liu dictionary and all neutral scores. Collapse the positive and negative texts into two larger documents.
```{r segregate, echo=TRUE, eval=TRUE}
positivetone<-toneofdocument %>%
  filter(toneofdocument>0) %>%
  select(tweet)
positivetext<-paste(unlist(positivetone$tweet), collapse=" ")
negativetone<-toneofdocument %>%
  filter(toneofdocument<0) %>%
  select(tweet)
negativetext<-paste(unlist(negativetone$tweet), collapse=" ")
```

### Comparison Wordcloud

Generate comparison cloud showing the most-frequent positive and negative words, where document 1 denotes positive texts, and document 2 denotes negative texts.
```{r comparison word cloud, echo=TRUE, eval=TRUE}
doc_id<-c("Frequent words in positive sentiment tweets","Frequent words in negative sentiment tweets")
line<-c(1,1)
comparisontext<-data.frame(doc_id, text=c(positivetext, negativetext),line, stringsAsFactors=FALSE)
df_source<-DataframeSource(comparisontext)
df_corpus<-VCorpus(df_source)
corpuscomparison_clean<-clean_corpus(df_corpus)
corpuscomparison_tdm<-TermDocumentMatrix(corpuscomparison_clean)
corpuscomparison_m<-as.matrix(corpuscomparison_tdm)
set.seed(2105)
comparison.cloud(corpuscomparison_m, colors=c("orange", "purple"), scale=c(0.1,2), title.size=1, max.words=100)
```

## (c) Get in their mind

Identify emotions (anger, anticipation, disgust, fear, sadness, sadness, surprise, trust) as well as negative and positive using the NRC Word-Emotion Association Lexicon in the `tidytext` package.
```{r NRC, echo=TRUE, eval=TRUE}
nrc_anger<-get_sentiments("nrc") %>% 
  filter(sentiment=="anger")
nrc_anticipation<-get_sentiments("nrc") %>% 
  filter(sentiment=="anticipation")
nrc_disgust<-get_sentiments("nrc") %>% 
  filter(sentiment=="disgust")
nrc_fear<-get_sentiments("nrc") %>% 
  filter(sentiment=="fear")
nrc_joy<-get_sentiments("nrc") %>% 
  filter(sentiment=="joy")
nrc_sadness<-get_sentiments("nrc") %>% 
  filter(sentiment=="sadness")
nrc_surprise<-get_sentiments("nrc") %>% 
  filter(sentiment=="surprise")
nrc_trust<-get_sentiments("nrc") %>% 
  filter(sentiment=="trust")
nrc_negative<-get_sentiments("nrc") %>% 
  filter(sentiment=="negative")
nrc_positive<-get_sentiments("nrc") %>% 
  filter(sentiment=="positive")
```

```{r}
nrc_anger$word
```

```{r}
angryf<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  angercount<-sum(tok[[1]] %in% nrc_anger$word)
  angerf<-angercount/wordcount
  return(angerf)
}
anticipationf<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  anticipationcount<-sum(tok[[1]] %in% nrc_anticipation$word)
  anticipationf<-anticipationcount/wordcount
  return(anticipationf)
}  
disgustf<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  disgustcount<-sum(tok[[1]] %in% nrc_disgust$word)
  disgustf<-disgustcount/wordcount
  return(disgustf)
}
fearf<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  fearcount<-sum(tok[[1]] %in% nrc_fear$word)
  fearf<-fearcount/wordcount
  return(fearf)
}
joyf<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  joycount<-sum(tok[[1]] %in% nrc_joy$word)
  joyf<-joycount/wordcount
  return(joyf)
}
sadnessf<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  sadnesscount<-sum(tok[[1]] %in% nrc_surprise$word)
  sadnessf<-sadnesscount/wordcount
  return(sadnessf)
}
surprisef<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  surprisecount<-sum(tok[[1]] %in% nrc_sadness$word)
  surprisef<-surprisecount/wordcount
  return(surprisef)
}
trustf<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  trustcount<-sum(tok[[1]] %in% nrc_trust$word)
  trustf<-trustcount/wordcount
  return(trustf)
}
negativef<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  negativecount<-sum(tok[[1]] %in% nrc_negative$word)
  negativef<-negativecount/wordcount
  return(negativef)
}
positivef<-function(words=c("Check out the frequency of words that represent emotions")){
  tok<-tokens(words)
  wordcount<-length(tok[[1]])
  positivecount<-sum(tok[[1]] %in% nrc_positive$word)
  positivef<-positivecount/wordcount
  return(positivef)
}
```

```{r}
emotionsfrequency<-Tesla
for (i in 1:126){
  emotionsfrequency$angryf[i]<-angryf(emotionsfrequency$tweet[i])
  emotionsfrequency$anticipationf[i]<-anticipationf(emotionsfrequency$tweet[i])
  emotionsfrequency$disgustf[i]<-disgustf(emotionsfrequency$tweet[i])
  emotionsfrequency$fearf[i]<-fearf(emotionsfrequency$tweet[i])
  emotionsfrequency$joyf[i]<-joyf(emotionsfrequency$tweet[i])
  emotionsfrequency$sadnessf[i]<-sadnessf(emotionsfrequency$tweet[i])
  emotionsfrequency$surprisef[i]<-surprisef(emotionsfrequency$tweet[i])
  emotionsfrequency$trustf[i]<-trustf(emotionsfrequency$tweet[i])
  emotionsfrequency$negativef[i]<-negativef(emotionsfrequency$tweet[i])
  emotionsfrequency$positivef[i]<-positivef(emotionsfrequency$tweet[i])
  
  emotionsfrequency$langryf[i]<-log(emotionsfrequency$angryf[i]+1)
  emotionsfrequency$lanticipationf[i]<-log(emotionsfrequency$anticipationf[i]+1)
  emotionsfrequency$ldisgustf[i]<-log(emotionsfrequency$disgustf[i]+1)
  emotionsfrequency$lfearf[i]<-log(emotionsfrequency$fearf[i]+1)
  emotionsfrequency$ljoyf[i]<-log(emotionsfrequency$joyf[i]+1)
  emotionsfrequency$lsadnessf[i]<-log(emotionsfrequency$sadnessf[i]+1)
  emotionsfrequency$lsurprisef[i]<-log(emotionsfrequency$surprisef[i]+1)
  emotionsfrequency$ltrustf[i]<-log(emotionsfrequency$trustf[i]+1)
  emotionsfrequency$lnegativef[i]<-log(emotionsfrequency$negativef[i]+1)
  emotionsfrequency$lpositivef[i]<-log(emotionsfrequency$positivef[i]+1)
}
emotionsfrequency
```

```{r write csv emotions, echo=TRUE, eval=TRUE}
write.csv(emotionsfrequency,"/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Tesla frequency of emotions.csv", row.names = FALSE)
```

```{r visualize the emotion relationship, echo=TRUE, eval=TRUE}
plotangry<-emotionsfrequency %>%
  ggplot(aes(x=langryf,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of angry words in the text (Log)", y="Daily stock price change", title="Relationship between Angry emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotangry
#ggsave('Angry-linear.png')
```

```{r}
plotanticipation<-emotionsfrequency %>%
  ggplot(aes(x=lanticipationf,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of anticipation words in the text (Log)", y="Daily stock price change", title="Relationship between Anticipation emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotanticipation
#ggsave('Anticipation-linear.png')
```

```{r}
plotdisgust<-emotionsfrequency %>%
  ggplot(aes(x=ldisgustf,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of disgust words in the text (Log)", y="Daily stock price change", title="Relationship between Disgust emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotdisgust
#ggsave('Disgust-linear.png')
```

```{r}
plotjoy<-emotionsfrequency %>%
  ggplot(aes(x=ljoyf,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of joy words in the text (Log)", y="Daily stock price change", title="Relationship between Joy emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotjoy
#ggsave('Joy-linear.png')
```

```{r}
plotfear<-emotionsfrequency %>%
  ggplot(aes(x=lfearf,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of fear words in the text (Log)", y="Daily stock price change", title="Relationship between Fear emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotfear
#ggsave('Fear-linear.png')
```

```{r}
plotsadness<-emotionsfrequency %>%
  ggplot(aes(x=lsadnessf,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of sadness words in the text (Log)", y="Daily stock price change", title="Relationship between Sadness emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotsadness
#ggsave('Sadness-linear.png')
```

```{r}
plotsurprise<-emotionsfrequency %>%
  ggplot(aes(x=lsurprisef,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of sadness words in the text (Log)", y="Daily stock price change", title="Relationship between Surprise emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotsurprise
#ggsave('Surprise-linear.png')
```

```{r}
plottrust<-emotionsfrequency %>%
  ggplot(aes(x=ltrustf,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of trust words in the text (Log)", y="Daily stock price change", title="Relationship between Trust emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plottrust
#ggsave('Trust-linear.png')
```

```{r}
plotnegative<-emotionsfrequency %>%
  ggplot(aes(x=lnegativef,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of negative words in the text (Log)", y="Daily stock price change", title="Relationship between Negative emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotnegative
#ggsave('Negative-linear.png')
```

```{r}
plotpositive<-emotionsfrequency %>%
  ggplot(aes(x=lpositivef,y=DailyChange))+
  geom_jitter(color="#00CED1")+
  geom_smooth(method="lm", se=FALSE, color="red")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="Frequency of positive words in the text (Log)", y="Daily stock price change", title="Relationship between Positive emotions and Daily Stock Price Change")+
  theme(plot.title=element_text(hjust=0.5))+
  theme(axis.text.x=element_text(hjust=0.5))
plotpositive
#ggsave('Positive-linear.png')
```

Linear regression
```{r}
emotionsfrequency$DailyChange<-as.numeric(emotionsfrequency$DailyChange)
lm<-lm(DailyChange ~ angryf+anticipationf+disgustf+fearf+joyf+sadnessf+surprisef+trustf+negativef+positivef, data=emotionsfrequency)
summary(lm)
```

```{r}
llm<-lm(DailyChange ~ langryf+lanticipationf+ldisgustf+lfearf+ljoyf+lsadnessf+lsurprisef+ltrustf+lnegativef+lpositivef, data=emotionsfrequency)
summary(llm)
```

```{r}
emotionsfrequency$DailyChange<-as.numeric(emotionsfrequency$DailyChange)
lmangry<-lm(DailyChange ~ angryf, data=emotionsfrequency)
summary(lmangry)
```

```{r}
emotionsfrequency$DailyChange<-as.numeric(emotionsfrequency$DailyChange)
llmangry<-lm(DailyChange ~ langryf, data=emotionsfrequency)
summary(llmangry)
```

```{r}
lmanticipation<-lm(DailyChange ~ anticipationf, data=emotionsfrequency)
summary(lmanticipation)
```

```{r}
llmanticipation<-lm(DailyChange ~ lanticipationf, data=emotionsfrequency)
summary(llmanticipation)
```

```{r}
lmdisgust<-lm(DailyChange ~ disgustf, data=emotionsfrequency)
summary(lmdisgust)
```

```{r}
llmdisgust<-lm(DailyChange ~ ldisgustf, data=emotionsfrequency)
summary(llmdisgust)
```

```{r}
lmfear<-lm(DailyChange ~ fearf, data=emotionsfrequency)
summary(lmfear)
```

```{r}
llmfear<-lm(DailyChange ~ lfearf, data=emotionsfrequency)
summary(llmfear)
```

```{r}
lmjoy<-lm(DailyChange ~ joyf, data=emotionsfrequency)
summary(lmjoy)
```

```{r}
llmjoy<-lm(DailyChange ~ ljoyf, data=emotionsfrequency)
summary(llmjoy)
```

```{r}
lmsadness<-lm(DailyChange ~ sadnessf, data=emotionsfrequency)
summary(lmsadness)
```

```{r}
llmsadness<-lm(DailyChange ~ lsadnessf, data=emotionsfrequency)
summary(llmsadness)
```

```{r}
lmsurprise<-lm(DailyChange ~ surprisef, data=emotionsfrequency)
summary(lmsurprise)
```

```{r}
llmsurprise<-lm(DailyChange ~ lsurprisef, data=emotionsfrequency)
summary(llmsurprise)
```

```{r}
lmtrust<-lm(DailyChange ~ trustf, data=emotionsfrequency)
summary(lmtrust)
```

```{r}
llmtrust<-lm(DailyChange ~ ltrustf, data=emotionsfrequency)
summary(llmtrust)
```

```{r}
lmnegative<-lm(DailyChange ~ negativef, data=emotionsfrequency)
summary(lmnegative)
```

```{r}
llmnegative<-lm(DailyChange ~ lnegativef, data=emotionsfrequency)
summary(llmnegative)
```

```{r}
lmpositive<-lm(DailyChange ~ positivef, data=emotionsfrequency)
summary(lmpositive)
```

```{r}
llmpositive<-lm(DailyChange ~ lpositivef, data=emotionsfrequency)
summary(llmpositive)
```

```{r}
library(stargazer)
stargazer(llm, type="text", title="Emotion Analysis: Multilinear Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Multilinear Regression Result (Log).txt")
stargazer(llm, type="text", title="Emotion Analysis: Multilinear Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Multilinear Regression Result (Log).pdf")
```

```{r}
library(stargazer)
stargazer(lm, type="text", title="Emotion Analysis: Multilinear Regression Result", digits=1, out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis:Multilinear Regression Result.txt")
```

```{r}
stargazer(llmangry, llmanticipation, llmdisgust, llmfear, llmjoy, llmsadness, llmsurprise, llmtrust, llmpositive, llmnegative,  type="text", title="Emotion Analysis:Linear Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Linear Regression Result (Log).txt")
```

```{r}
stargazer(lmangry, lmanticipation, lmdisgust, lmfear, lmjoy, lmsadness, lmsurprise, lmtrust, lmpositive, lmnegative,  type="text", title="Emotion Analysis:Linear Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Linear Regression Result.txt")
```


Prepare corpus for identifying emotions.

For tweets that are associated with daily stock price increase/decrease:
```{r}
iTesla<-Tesla %>%
  filter(DailyChange>0)
dTesla<-Tesla %>%
  filter(DailyChange<0)
```

```{r prepare corpus for identifying emotions}
#Increasing daily stock prices
doc_id<-c(1:80)
line<-c(rep(1,80))
text<-data.frame(doc_id, text=c(iTesla$tweet),line, stringsAsFactors=FALSE)
i_df_source<-DataframeSource(text)
i_df_nrc<-VCorpus(i_df_source)
i_nrc_clean<-clean_corpus(i_df_nrc)
i_nrc_dtm<-DocumentTermMatrix(i_nrc_clean)
i_nrc_m<-as.matrix(i_nrc_dtm)
i_nrc_td<-tidy(i_nrc_dtm)
i_nrc_tf_idf<-i_nrc_td %>%
  bind_tf_idf(term, document, count)
i_nrc_tf_idf<-i_nrc_tf_idf %>%
  arrange(desc(tf_idf))
i_nrc_tf_idf
```

```{r prepare corpus 2nd for identifying emotions}
#Decreasing daily stock prices
doc_id<-c(1:46)
line<-c(rep(1,46))
text<-data.frame(doc_id, text=c(dTesla$tweet),line, stringsAsFactors=FALSE)
d_df_source<-DataframeSource(text)
d_df_nrc<-VCorpus(d_df_source)
d_nrc_clean<-clean_corpus(d_df_nrc)
d_nrc_dtm<-DocumentTermMatrix(d_nrc_clean)
d_nrc_m<-as.matrix(d_nrc_dtm)
d_nrc_td<-tidy(d_nrc_dtm)
d_nrc_tf_idf<-d_nrc_td %>%
  bind_tf_idf(term, document, count)
d_nrc_tf_idf<-d_nrc_tf_idf %>%
  arrange(desc(tf_idf))
d_nrc_tf_idf
```

### Angry

Find tf_idf score for angry words used in the tweets.
```{r anger, echo=TRUE, eval=TRUE}
ianger<-i_nrc_tf_idf %>%
  filter(term %in% nrc_anger$word) %>%
  select(term,tf_idf)
ianger<-rename(ianger, i_tf_idf=tf_idf)
danger<-d_nrc_tf_idf %>%
  filter(term %in% nrc_anger$word) %>%
  select(term,tf_idf)
danger<-rename(danger, d_tf_idf=tf_idf)
angerwords<-full_join(ianger, danger,by="term")
#Replace all NA values as 0
angerwords$i_tf_idf[is.na(angerwords$i_tf_idf)]<-0
angerwords$d_tf_idf[is.na(angerwords$d_tf_idf)]<-0
angerwords
```

Visualize the relationship between the use of words from the angry category and stock price change. 
```{r plot anger, echo=TRUE, eval=TRUE}
plot2<-angerwords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(angry words) in tweets associated with stock price increase", y="f(angry words) in tweets associated with stock price decrease", title="Frequency of angry words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,3), breaks=seq(0,3,0.5))+
  scale_y_continuous(limits=c(0,3), breaks=seq(0,3,0.5))#+
  #facet_zoom(x=i_tf_idf<=0.5, y=d_tf_idf<=0.5)
plot2
#ggsave('angry diff.png')
```

### Anticipation

Find tf_idf score for anticipation words used in the tweets.
```{r anticipation, echo=TRUE, eval=TRUE}
ianticipation<-i_nrc_tf_idf %>%
  filter(term %in% nrc_anticipation$word) %>%
  select(term,tf_idf)
ianticipation<-rename(ianticipation, i_tf_idf=tf_idf)
danticipation<-d_nrc_tf_idf %>%
  filter(term %in% nrc_anticipation$word) %>%
  select(term,tf_idf)
danticipation<-rename(danticipation, d_tf_idf=tf_idf)
anticipationwords<-full_join(ianticipation, danticipation,by="term")
#Replace all NA values as 0
anticipationwords$i_tf_idf[is.na(anticipationwords$i_tf_idf)]<-0
anticipationwords$d_tf_idf[is.na(anticipationwords$d_tf_idf)]<-0
anticipationwords
```

Visualize the relationship between the use of words from the anticipation category and stock price change. 
```{r plot anticipation, echo=TRUE, eval=TRUE}
plot3<-anticipationwords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(anticipation words) in tweets associated with stock price increase", y="f(anticipation words) in tweets associated with stock price decrease", title="Frequency of anticipation words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,3), breaks=seq(0,3,0.5))+
  scale_y_continuous(limits=c(0,3), breaks=seq(0,3,0.5))
plot3
#ggsave('anticipation diff.png')
```

### Disgust

Find tf_idf score for disgust words used in the tweets.
```{r disgust, echo=TRUE, eval=TRUE}
idisgust<-i_nrc_tf_idf %>%
  filter(term %in% nrc_disgust$word) %>%
  select(term,tf_idf)
idisgust<-rename(idisgust, i_tf_idf=tf_idf)
ddisgust<-d_nrc_tf_idf %>%
  filter(term %in% nrc_disgust$word) %>%
  select(term,tf_idf)
ddisgust<-rename(ddisgust, d_tf_idf=tf_idf)
disgustwords<-full_join(idisgust, ddisgust,by="term")
#Replace all NA values as 0
disgustwords$i_tf_idf[is.na(disgustwords$i_tf_idf)]<-0
disgustwords$d_tf_idf[is.na(disgustwords$d_tf_idf)]<-0
disgustwords
```

Visualize the relationship between the use of words from the disgust category and stock price change 
```{r plot disgust, echo=TRUE, eval=TRUE}
plot4<-disgustwords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(disgust words) in tweets associated with stock price increase", y="f(disgust words) in tweets associated with stock price decrease", title="Frequency of disgust words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,2), breaks=seq(0,2,0.5))+
  scale_y_continuous(limits=c(0,2), breaks=seq(0,2,0.5))
plot4
#ggsave('disgust diff.png')
```

### Fear

Find tf_idf score for fear words used in the tweets.
```{r fear, echo=TRUE, eval=TRUE}
ifear<-i_nrc_tf_idf %>%
  filter(term %in% nrc_fear$word) %>%
  select(term,tf_idf)
ifear<-rename(ifear, i_tf_idf=tf_idf)
dfear<-d_nrc_tf_idf %>%
  filter(term %in% nrc_fear$word) %>%
  select(term,tf_idf)
dfear<-rename(dfear, d_tf_idf=tf_idf)
fearwords<-full_join(ifear, dfear,by="term")
#Replace all NA values as 0
fearwords$i_tf_idf[is.na(fearwords$i_tf_idf)]<-0
fearwords$d_tf_idf[is.na(fearwords$d_tf_idf)]<-0
fearwords
```

Visualize the relationship between the use of words from the fear category and stock price change. 
```{r plot fear, echo=TRUE, eval=TRUE}
plot5<-fearwords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(fear words) in tweets associated with stock price increase", y="f(fear words) in tweets associated with stock price decrease", title="Frequency of fear words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,2), breaks=seq(0,2,0.5))+
  scale_y_continuous(limits=c(0,2), breaks=seq(0,2,0.5))
plot5
#ggsave('fear diff.png')
```

### Joy

Find tf_idf score for joy words used in the tweets.
```{r joy, echo=TRUE, eval=TRUE}
ijoy<-i_nrc_tf_idf %>%
  filter(term %in% nrc_joy$word) %>%
  select(term,tf_idf)
ijoy<-rename(ijoy, i_tf_idf=tf_idf)
djoy<-d_nrc_tf_idf %>%
  filter(term %in% nrc_joy$word) %>%
  select(term,tf_idf)
djoy<-rename(djoy, d_tf_idf=tf_idf)
joywords<-full_join(ijoy, djoy,by="term")
#Replace all NA values as 0
joywords$i_tf_idf[is.na(joywords$i_tf_idf)]<-0
joywords$d_tf_idf[is.na(joywords$d_tf_idf)]<-0
joywords
```

Visualize the relationship between the use of words from the joy category and stock price change.
```{r plot joy, echo=TRUE, eval=TRUE}
plot6<-joywords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(joy words) in tweets associated with stock price increase", y="f(joy words) in tweets associated with stock price decrease", title="Frequency of joy words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,3), breaks=seq(0,3,0.5))+
  scale_y_continuous(limits=c(0,3), breaks=seq(0,3,0.5))
plot6
#ggsave('joy diff.png')
```

### Sadness

Find tf_idf score for sadness words used in the tweets.
```{r sadness, echo=TRUE, eval=TRUE}
isadness<-i_nrc_tf_idf %>%
  filter(term %in% nrc_sadness$word) %>%
  select(term,tf_idf)
isadness<-rename(isadness, i_tf_idf=tf_idf)
dsadness<-d_nrc_tf_idf %>%
  filter(term %in% nrc_sadness$word) %>%
  select(term,tf_idf)
dsadness<-rename(dsadness, d_tf_idf=tf_idf)
sadnesswords<-full_join(isadness, dsadness,by="term")
#Replace all NA values as 0
sadnesswords$i_tf_idf[is.na(sadnesswords$i_tf_idf)]<-0
sadnesswords$d_tf_idf[is.na(sadnesswords$d_tf_idf)]<-0
sadnesswords
```

Visualize the relationship between the use of words from the sadness category and stock price change.
```{r plot sadness, echo=TRUE, eval=TRUE}
plot7<-sadnesswords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(sadness words) in tweets associated with stock price increase", y="f(sadness words) in tweets associated with stock price decrease", title="Frequency of sadness words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,2.5), breaks=seq(0,2.5,0.5))+
  scale_y_continuous(limits=c(0,2.5), breaks=seq(0,2.5,0.5))
plot7
#ggsave('sadness diff.png')
```
### Surprise

Find tf_idf score for surprise words used in the tweets.
```{r surprise, echo=TRUE, eval=TRUE}
isurprise<-i_nrc_tf_idf %>%
  filter(term %in% nrc_surprise$word) %>%
  select(term,tf_idf)
isurprise<-rename(isurprise, i_tf_idf=tf_idf)
dsurprise<-d_nrc_tf_idf %>%
  filter(term %in% nrc_surprise$word) %>%
  select(term,tf_idf)
dsurprise<-rename(dsurprise, d_tf_idf=tf_idf)
surprisewords<-full_join(isurprise, dsurprise,by="term")
#Replace all NA values as 0
surprisewords$i_tf_idf[is.na(surprisewords$i_tf_idf)]<-0
surprisewords$d_tf_idf[is.na(surprisewords$d_tf_idf)]<-0
surprisewords
```

Visualize the relationship between the use of words from the surprise category and stock price change.
```{r plot surprise, echo=TRUE, eval=TRUE}
plot8<-surprisewords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(surprise words) in tweets associated with stock price increase", y="f(surprise words) in tweets associated with stock price decrease", title="Frequency of surprise words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,2), breaks=seq(0,2,0.5))+
  scale_y_continuous(limits=c(0,2), breaks=seq(0,2,0.5))
plot8
#ggsave('surprise diff.png')
```

### Trust

Find tf_idf score for trust words used in the tweets.
```{r trust, echo=TRUE, eval=TRUE}
itrust<-i_nrc_tf_idf %>%
  filter(term %in% nrc_trust$word) %>%
  select(term,tf_idf)
itrust<-rename(itrust, i_tf_idf=tf_idf)
dtrust<-d_nrc_tf_idf %>%
  filter(term %in% nrc_trust$word) %>%
  select(term,tf_idf)
dtrust<-rename(dtrust, d_tf_idf=tf_idf)
trustwords<-full_join(itrust, dtrust,by="term")
#Replace all NA values as 0
trustwords$i_tf_idf[is.na(trustwords$i_tf_idf)]<-0
trustwords$d_tf_idf[is.na(trustwords$d_tf_idf)]<-0
trustwords
```

Visualize the relationship between the use of words from the trust category and stock price change.
```{r plot trust, echo=TRUE, eval=TRUE}
plot9<-trustwords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(trust words) in tweets associated with stock price increase", y="f(trust words) in tweets associated with stock price decrease", title="Frequency of trust words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,2), breaks=seq(0,2,0.5))+
  scale_y_continuous(limits=c(0,2), breaks=seq(0,2,0.5))
plot9
#ggsave('trust diff.png')
```

### Negative

Find tf_idf score for negative words used in the tweets.
```{r negative, echo=TRUE, eval=TRUE}
inegative<-i_nrc_tf_idf %>%
  filter(term %in% nrc_negative$word) %>%
  select(term,tf_idf)
inegative<-rename(inegative, i_tf_idf=tf_idf)
dnegative<-d_nrc_tf_idf %>%
  filter(term %in% nrc_negative$word) %>%
  select(term,tf_idf)
dnegative<-rename(dnegative, d_tf_idf=tf_idf)
negativewords<-full_join(inegative, dnegative,by="term")
#Replace all NA values as 0
negativewords$i_tf_idf[is.na(negativewords$i_tf_idf)]<-0
negativewords$d_tf_idf[is.na(negativewords$d_tf_idf)]<-0
negativewords
```

Visualize the relationship between the use of words from the negative category and stock price change.
```{r plot negative, echo=TRUE, eval=TRUE}
plot10<-negativewords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(negative words) in tweets associated with stock price increase", y="f(negative words) in tweets associated with stock price decrease", title="Frequency of negative words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,2), breaks=seq(0,2,0.5))+
  scale_y_continuous(limits=c(0,2), breaks=seq(0,2,0.5))
plot10
#ggsave('negative diff.png')
```

### Positive

Find tf_idf score for positive words used in the tweets.
```{r positive, echo=TRUE, eval=TRUE}
ipositive<-i_nrc_tf_idf %>%
  filter(term %in% nrc_positive$word) %>%
  select(term,tf_idf)
ipositive<-rename(ipositive, i_tf_idf=tf_idf)
dpositive<-d_nrc_tf_idf %>%
  filter(term %in% nrc_positive$word) %>%
  select(term,tf_idf)
dpositive<-rename(dpositive, d_tf_idf=tf_idf)
positivewords<-full_join(ipositive, dpositive,by="term")
#Replace all NA values as 0
positivewords$i_tf_idf[is.na(positivewords$i_tf_idf)]<-0
positivewords$d_tf_idf[is.na(positivewords$d_tf_idf)]<-0
positivewords
```

Visualize the relationship between the use of words from the positive category and stock price change.
```{r plot positive, echo=TRUE, eval=TRUE}
plot11<-positivewords %>%
  ggplot(aes(x=i_tf_idf,y=d_tf_idf))+
  geom_jitter(color="#00CED1")+
  theme_bw()+
  theme(legend.position="none")+
  labs(x="f(positive words) in tweets associated with stock price increase", y="f(positive words) in tweets associated with stock price decrease", title="Frequency of positive words in tweets associated with stock price increase/decrease")+
  theme(plot.title=element_text(hjust=0.5))+
  scale_x_continuous(limits=c(0,3), breaks=seq(0,3,0.5))+
  scale_y_continuous(limits=c(0,3), breaks=seq(0,3,0.5))
plot11
#ggsave('positive diff.png')
```

Logistic Regression

```{r}
emotionsfrequency$Direction[emotionsfrequency$DailyChange>0]<-1
emotionsfrequency$Direction[emotionsfrequency$DailyChange==0]<-0
emotionsfrequency$Direction[emotionsfrequency$DailyChange<0]<--1
emotionsfrequency$Direction<-as.factor(emotionsfrequency$Direction)
emotionsfrequency
```

```{r}
logit<-glm(Direction ~ angryf+anticipationf+disgustf+fearf+joyf+sadnessf+surprisef+trustf+negativef+positivef, emotionsfrequency, family=binomial(link ="logit"))
summary(logit)
```

```{r}
stargazer(logit, type="text", title="Emotion Analysis: Multi-logistic Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Multi-logistic Regression Result.txt")
```

```{r}
llogit<-glm(Direction ~ langryf+lanticipationf+ldisgustf+lfearf+ljoyf+lsadnessf+lsurprisef+ltrustf+lpositivef+lnegativef, emotionsfrequency, family=binomial(link ="logit"))
summary(llogit)
```

```{r}
stargazer(llogit, type="text", title="Emotion Analysis: Multi-logistic Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Multi-logistic Regression Result (Log).txt")
```

```{r}
logitangry<-glm(Direction ~ angryf, emotionsfrequency, family=binomial(link ="logit"))
summary(logitangry)
```

```{r}
llogitangry<-glm(Direction ~ langryf, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitangry)
```

```{r}
logitanticipation<-glm(Direction ~ anticipationf, emotionsfrequency, family=binomial(link ="logit"))
summary(logitanticipation)
```

```{r}
llogitanticipation<-glm(Direction ~ lanticipationf, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitanticipation)
```

```{r}
logitdisgust<-glm(Direction ~ disgustf, emotionsfrequency, family=binomial(link ="logit"))
summary(logitdisgust)
```

```{r}
llogitdisgust<-glm(Direction ~ ldisgustf, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitdisgust)
```

```{r}
logitfear<-glm(Direction ~ fearf, emotionsfrequency, family=binomial(link ="logit"))
summary(logitfear)
```

```{r}
llogitfear<-glm(Direction ~ lfearf, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitfear)
```

```{r}
logitjoy<-glm(Direction ~ joyf, emotionsfrequency, family=binomial(link ="logit"))
summary(logitjoy)
```

```{r}
llogitjoy<-glm(Direction ~ ljoyf, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitjoy)
```

```{r}
logitsadness<-glm(Direction ~ sadnessf, emotionsfrequency, family=binomial(link ="logit"))
summary(logitsadness)
```

```{r}
llogitsadness<-glm(Direction ~ lsadnessf, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitsadness)
```

```{r}
logitsurprise<-glm(Direction ~ surprisef, emotionsfrequency, family=binomial(link ="logit"))
summary(logitsurprise)
```

```{r}
llogitsurprise<-glm(Direction ~ lsurprisef, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitsurprise)
```

```{r}
logitsurprise<-glm(Direction ~ surprisef, emotionsfrequency, family=binomial(link ="logit"))
summary(logitsurprise)
```

```{r}
llogitsurprise<-glm(Direction ~ lsurprisef, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitsurprise)
```

```{r}
logittrust<-glm(Direction ~ trustf, emotionsfrequency, family=binomial(link ="logit"))
summary(logittrust)
```

```{r}
llogittrust<-glm(Direction ~ ltrustf, emotionsfrequency, family=binomial(link ="logit"))
summary(llogittrust)
```

```{r}
logitnegative<-glm(Direction ~ negativef, emotionsfrequency, family=binomial(link ="logit"))
summary(logitnegative)
```

```{r}
llogitnegative<-glm(Direction ~ lnegativef, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitnegative)
```

```{r}
logitpositive<-glm(Direction ~ positivef, emotionsfrequency, family=binomial(link ="logit"))
summary(logitpositive)
```

```{r}
llogitpositive<-glm(Direction ~ lpositivef, emotionsfrequency, family=binomial(link ="logit"))
summary(llogitpositive)
```

```{r}
stargazer(logitangry, logitanticipation, logitdisgust, logitfear, logitjoy, logitsadness, logitsurprise, logittrust, logitpositive, logitnegative,  type="text", title="Emotion Analysis: Logistic Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Logistic Regression Result.txt")
```

```{r}
stargazer(llogitangry, llogitanticipation, llogitdisgust, llogitfear, llogitjoy, llogitsadness, llogitsurprise, llogittrust, llogitpositive, llogitnegative,  type="text", title="Emotion Analysis: Logistic Regression Result", out="/Users/annie/Desktop/Columbia Fall2021/Columbia Course Fall 2021/GR5067 NLP/Group Project/Tesla/Emotion Analysis: Logistic Regression Result (Log).txt")
```